|

### 2021-08-07 prova_knit_finale.Rmd
Aggiornato con x/2

We are now ready to compare the performances of these four algorithms. We simulate a Stochastic Volatility process setting arbitrarily the following parameters: $\alpha = -0.1$, $\beta = 0.9$ and $\tau^{2}=0.01$. The resulting observation and state process is shown in the figure below.

```{r include=FALSE}
# Simulating the data
# -------------------
set.seed(12345)
n     =  50
alpha =  0
beta  =  0.9
tau2  =  0.01
tau   = sqrt(tau2)
y     = rep(0,n)
x     = rep(0,n)
x[1]  = alpha/(1-beta)
y[1]  = rnorm(1,0,exp(x[1]))
for (t in 2:n){
  x[t] = alpha + beta*x[t-1] + rnorm(1,0,tau)
  y[t] = rnorm(1,0,exp(x[t]))
}
alpha.true = alpha
beta.true  = beta
tau2.true  = tau2

@@

    x<-rnorm(N,alpha+beta*x,tau)
    w1<-w*dnorm(data[t],0,exp(x))

@@

    xprev<-x
    x<-rnorm(N,alpha+beta*x+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*x))-2),tau)
    w1<-w*dnorm(data[t],0,exp(x))*dnorm(x,alpha+beta*xprev,tau)/
      dnorm(x,mean=alpha+beta*xprev+(tau^2)/4*((data[t]^2)*exp(-(alpha+beta*xprev))-2),tau)

@@

    vpar     = var(pars)
    ms          = a*pars+(1-a)*matrix(mpar,N,3,byrow=T)
    mus         = pars[,1]+pars[,2]*xs 
    weight      = w*dnorm(data[t],0,exp(mus))
    k           = sample(1:N,size=N,replace=T,prob=weight)
    ms1         = ms[k,] + matrix(rnorm(3*N),N,3)%*%chol(h2*vpar)
    xt          = rnorm(N,ms1[,1]+ms1[,2]*xs[k],exp(ms1[,3]/2))
    w           = dnorm(data[t],0,exp(xt))/dnorm(data[t],0,exp(mus[k]))
    w           = w/sum(w)
    ESS         = 1/sum(w^2)

@@

```{r include=FALSE}
N <- 5000
alpha <- 0
beta  <-  0.9
tau2  =  0.01
tau   = sqrt(tau2)
m0      = 0
C0      = 100
ealpha  = alpha
valpha  = 0.01
ebeta    = beta
vbeta    = 0.01
nu      = 3
lambda  = tau2

>>>>

We are now ready to compare the performances of these four algorithms. We simulate a Stochastic Volatility process setting arbitrarily the following parameters: $\alpha = 0$, $\beta = 0.99$ and $\tau^{2}=0.05$. The resulting observation and state process is shown in the figure below.

```{r include=FALSE}
# Simulating the data
# -------------------
set.seed(12345)
n     =  50
alpha =  0
beta  =  0.99
tau2  =  0.05
tau   = sqrt(tau2)
y     = rep(0,n)
x     = rep(0,n)
x[1]  = alpha/(1-beta)
y[1]  = rnorm(1,0,exp(x[1]))
for (t in 2:n){
  x[t] = alpha + beta*x[t-1] + rnorm(1,0,tau)
  y[t] = rnorm(1,0,exp(x[t]))
}
alpha.true = alpha
beta.true  = beta
tau2.true  = tau2

@@

@@

@@

@@

```{r include=FALSE}
N <- 5000
alpha <- 0
beta  <-  0.99
tau2  =  0.05
tau   = sqrt(tau2)
m0      = 0
C0      = 100
ealpha  = alpha
valpha  = 0.01
ebeta    = beta
vbeta    = 0.01
nu      = 5
lambda  = tau2*3/5
